---
title: "Human Resources"
output:
    flexdashboard::flex_dashboard:
        logo: www/tns-logo-small.png
        orientation: columns
        theme: 
            bootswatch: "lux"
            bg: "white"
            fg: "black"
            primary: "#a087ae"
            secondary: "#a087ae"
runtime: shiny
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo    = FALSE,
    message = FALSE,
    warning = FALSE
)

# SHINY
library(shiny)
library(shinyjs)
library(shinyFiles)

# Getting Text from PDF/Images
library(tesseract)
library(pdftools)
library(magick)

# Text Analysis
library(tidytext)
library(SnowballC)

# Visualization
library(tidyquant)
library(plotly)
library(wordcloud2)

# Core Analysis
library(tidyverse)
```

``` {css}
.chart-title {
  background-color: white;
  color: black;
}

.chart-stage {
  background-color: white;
}

.section.sidebar {
  background-color: white;
}

.navbar.navbar-inverse {
  background-color: #a087ae!important;
  box-shadow: 3px 3px 5px white;
}

.navbar-dark .navbar-brand, .navbar.navbar-inverse .navbar-brand {
  color:white;
}

.navbar.navbar-inverse ul.nav.navbar-nav>li.active>a {
  color:white;
}

.dashboard-column {
  background-color: white;
}

.section {
  background-color: white;
}

body {
  background-color:white;
}

.selectize-dropdown {
  background-color:white;
}
.selectize-input.full {
  background-color:white;
}
.selectize-input, .selectize-control.single .selectize-input.input-active {
  background-color:white;
}
.selectize-dropdown .active {
  background-color: #a087ae;
  color: #f2f2f2;
}

.form-control {
    background-color:white;
}
.form-control:active{
    background-color:white;
}
.form-control:hover{
    background-color:white;
}
.form-control:focus{
    background-color:white;
}

.datepicker {
    background-color:white;
}
.datepicker .datepicker-switch:hover, .datepicker .prev:hover, .datepicker .next:hover, .datepicker tfoot tr th:hover {
    background-color:#a087ae;
}
.datepicker table tr td.day:hover {
    background-color:#a087ae;
}
.datepicker table tr td.month:hover {
    background-color:#a087ae;
}
.datepicker table tr td.year:hover {
    background-color:#a087ae;
}

.nav-tabs .nav-link.active, .nav-tabs>li>a.active {
    background-color:#a087ae;
}

.modal-content {
  background-color: white;
}

```

```{css}
#resume_first_page {
  overflow: scroll;
}
```



# Resume Analysis

## Column {.sidebar}

#### What does the app do?
> Uses Natural Language Processing to detect the main skills of a job applicant. 

<hr>


#### Resume Controls
```{r}

useShinyjs(rmd = TRUE)

renderUI({
  shinyFiles::shinyFilesButton(
    id       = "resume_file",
    label    = "Import a Resume (PDF)",
    title    = "Please select a File",
    multiple = FALSE
  )
})

shiny::sliderInput(
  inputId = "max_width",
  label = "Image Max Width %",
  min = 10,
  max = 200,
  value = 100
)
```


```{r}
rv <- reactiveValues()

volumes <- c(root='.')

shinyFiles::shinyFileChoose(
  input, 
  id        = 'resume_file', 
  root      = volumes, 
  session   = session,
  filetypes = c('pdf')
)

observe({
  
  print(input$resume_file)
  
  if (is.null(input$resume_file)) {
    cat("No files have been selected (shinyFileChoose)")
  } else if (is.integer(input$resume_file)) {
    cat("No files have been selected (shinyFileChoose)")
  } else {
    
    rv$file_path_tbl <- parseFilePaths(volumes, input$resume_file)
    
    print(rv$file_path_tbl)
    
    
    # process first page of image for preview
    resume_first_page <- pdftools::pdf_convert(
      pdf        = rv$file_path_tbl$datapath, 
      filenames  = "images/resume-app.png",
      pages      = 1,
      dpi        = 600)
    
    rv$image_path <- "images/resume-app.png"
    
    
    # Process all pages for OCR
    resume_full_image <- pdftools::pdf_convert(
        pdf        = rv$file_path_tbl$datapath, 
        filenames  = ,
        pages      = NULL,
        dpi        = 600)
    
    # OCR
    resume_text <- tesseract::ocr(resume_full_image)
    
    # Text Processing
    resume_tbl <- tibble(
      resume_id = 1,
      text      = resume_text
    )
    
    ngrams_multiple_tbl <- resume_tbl %>%
      unnest_tokens(
        output   = word,
        input    = text,
        to_lower = TRUE,
        token    = "ngrams",
        n        = 3,
        n_min    = 1,
        # Passed to tokenizers::tokenize_ngrams()
        stopwords = stop_words %>% filter(!word == "r") %>% pull(word))
    
    # TF-IDF
    rv$ngrams_tf_tbl <- ngrams_multiple_tbl %>%
      group_by(resume_id) %>%
      count(word, sort = TRUE) %>%
      ungroup() %>%
      filter(!str_detect(word, pattern = "[0-9]")) 
    
    rv$ngrams_tfidf_tbl <- rv$ngrams_tf_tbl %>%
      bind_tf_idf(
        term     = word, 
        document = resume_id, 
        n        = n
      )

    
  }
  
})
```


## Column

### Resume Preview (page 1 only)
```{r}
output$resume_first_page <- renderImage({

  req(rv$file_path_tbl)
  req(rv$file_path_tbl$datapath)
  req(input$max_width)

  # image_read(rv$file_path_tbl$datapath) %>%
  #   image_scale("800")

  list(
    src   = rv$image_path,
    style = str_glue("max-width:{input$max_width}%;")
  )

}, deleteFile = FALSE)

shiny::imageOutput("resume_first_page")
```


## Column

### Word Cloud
```{r}
output$word_cloud <- renderWordcloud2({
  
  req(rv$ngrams_tfidf_tbl)
  
  rv$ngrams_tfidf_tbl %>%
    select(word, n) %>%
    rename(freq = n) %>%
    wordcloud2(
        size = 1.5,
        color = palette_light() %>% unname() %>% rep(4)
    )
  
})

wordcloud2::wordcloud2Output("word_cloud")
```


### Top 25 Words
```{r}
output$plotly_1 <- renderPlotly({

  req(rv$ngrams_tfidf_tbl)

  rv$ngrams_tfidf_tbl %>%
    slice(1:25) %>%
    mutate(word = fct_reorder(word, tf)) %>%
    mutate(desc = str_glue("word: {word}
                           term-frequency: {scales::percent(tf)}
                           term-count: {n}")) %>%
    ggplot(aes(word, tf, fill = tf)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_tq()

})

plotlyOutput(outputId = "plotly_1")
```




# Job Description Analysis
## Column {.sidebar}
<br>

#### What does the app do?

> Uses Natural Language Processing to detect the main skills of a job applicant. 

<hr>


#### Job Description Controls
```{r}
renderUI({
  shinyFiles::shinyFilesButton(
    id       = "job_file",
    label    = "Import a Job Description (PDF)",
    title    = "Please select a File",
    multiple = FALSE
  )
})

shiny::sliderInput(
  inputId = "max_width_job",
  label = "Image Max Width %",
  min = 10,
  max = 200,
  value = 100
)
```


```{r}
rv <- reactiveValues()

volumes <- c(root='.')

shinyFiles::shinyFileChoose(
  input, 
  id        = 'job_file', 
  root      = volumes, 
  session   = session,
  filetypes = c('pdf')
)

observe({
  
  print(input$job_file)
  
  if (is.null(input$job_file)) {
    cat("No files have been selected (shinyFileChoose)")
  } else if (is.integer(input$job_file)) {
    cat("No files have been selected (shinyFileChoose)")
  } else {
    
    rv$job_file_path_tbl <- parseFilePaths(volumes, input$job_file)
    
    print(rv$job_file_path_tbl)
    
    
    # process first page of image for preview
    job_image <- pdftools::pdf_convert(
      pdf        = rv$job_file_path_tbl$datapath, 
      pages      = 1,
      filenames  = "images/job-app.png",
      dpi        = 600)
    
    rv$job_image_path <- "images/job-app.png"
    
    
    # Process all pages for OCR
    job_full_image <- pdftools::pdf_convert(
        pdf        = rv$job_file_path_tbl$datapath, 
        filenames  = ,
        pages      = NULL,
        dpi        = 600)
    
    # OCR
    job_text <- tesseract::ocr(job_full_image)
    
    # Text Processing
    job_tbl <- tibble(
      job_id = 1,
      text   = job_text
    )
    
    ngrams_job_tbl <- job_tbl %>%
      unnest_tokens(
        output   = word,
        input    = text,
        to_lower = TRUE,
        token    = "ngrams",
        n        = 3,
        n_min    = 1,
        stopwords = stop_words %>% filter(!word == "r") %>% pull(word))
    
    
    # TF-IDF
    rv$ngrams_job_tf_tbl <- ngrams_job_tbl %>%
      group_by(job_id) %>%
      count(word, sort = TRUE) %>%
      ungroup() %>%
      filter(!str_detect(word, pattern = "[0-9]")) 
    
    rv$ngrams_job_tfidf_tbl <- rv$ngrams_job_tf_tbl %>%
      bind_tf_idf(
        term     = word, 
        document = job_id, 
        n        = n
      )

    
  }
  
})
```



## Column

### Job Description Preview
```{r}
output$job_image <- renderImage({

  req(rv$job_file_path_tbl)
  req(rv$job_file_path_tbl$datapath)
  req(input$max_width_job)
  #
  # image_read(rv$file_path_tbl$datapath) %>%
  #   image_scale("800")

  list(
    src   = rv$job_image_path,
    style = str_glue("max-width:{input$max_width_job}%;")
  )

}, deleteFile = FALSE)

shiny::imageOutput("job_image")
```



## Column

### Word Cloud
```{r}
output$word_cloud_job <- renderWordcloud2({
  
  req(rv$ngrams_job_tfidf_tbl)
  
  rv$ngrams_job_tfidf_tbl %>%
    select(word, n) %>%
    rename(freq = n) %>%
    wordcloud2(
        size = 1.5,
        color = palette_light() %>% unname() %>% rep(4)
    )
  
})

wordcloud2::wordcloud2Output("word_cloud_job")
```








# Similarity Results

## Column

### Similarity Results
```{r}
output$prt <- shiny::renderText({

  req(rv$ngrams_tf_tbl)
  req(rv$ngrams_job_desc_tf_tbl)

  # * Combine the data ----
  doc_tf_tbl <- bind_rows(
      rv$ngrams_tf_tbl %>%
          mutate(doc_id = 1) %>%
          select(doc_id, word, n) %>%
          slice(1:100)
      ,

      rv$ngrams_job_desc_tf_tbl %>%
          mutate(doc_id = 2) %>%
          select(doc_id, word, n) %>%
          slice(1:100)
  )

  # * Convert to Wide ----
  doc_tf_wide_tbl <- doc_tf_tbl %>%
      pivot_wider(
          id_cols     = word,
          names_from  = doc_id,
          values_from = n,
          values_fill = 0,
          names_prefix = "doc_"
      )

  # * Calculate Cosine Similarity
  doc_tf_wide_tbl %>%
      select(-word) %>%
      as.matrix() %>%
      lsa::cosine()

})

shiny::verbatimTextOutput("prt")
```


